cleaning.qmd

### 2024-11-30 missing.qmd
Adding analysis code file

```{r}
library(dplyr)
library(tidyverse)
```

```{r}
combined <- read.csv('F24_STATS_FINAL/combined.csv')
```

@@

```{r}
combined %>%
           group_by(State) %>%
           summarise(total_count = n(), Income_NA_count = sum(is.na(Median.Household.Income)), Uninsured_NA_count = sum(is.na(Percent.Uninsured.Adults)), Tax_NA_count = sum(is.na(Median.Prop.Tax)), Segregation_NA_count = sum(is.na(Residential.Segregation.Index)), Foods_NA_count = sum(is.na(Percent.Limited.Access.Healthy.Foods)), Expectancy_NA_count = sum(is.na(Life.Expectancy)), Adequacy_NA_count = sum(is.na(School.Funding.Adequacy)))
```

@@

@@

sub <- combined |> select(c("Life.Expectancy","Residential.Segregation.Index","Percent.Limited.Access.Healthy.Foods","Percent.Uninsured.Adults","Median.Household.Income", "School.Funding.Cat", "Median.Prop.Tax"))
sub <- unlabel(sub) #unlabel the data (labels cause problem for the mice function)
sub.imp <- mice(sub, m=5, method="pmm", print=FALSE)
```

```{r}
sub.mods <- with(sub.imp, #replace with. model
)
summary(pool(sub.mods))

>>>>

```{r}
library(dplyr)
library(tidyverse)
library(Hmisc)
```

```{r}
combined <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/combined.csv')
```

@@

```{r}
combined <- combined %>%
    rename(
      "Perc.Uninsured.Adults" = "X..Uninsured.Adults",
      "Perc.Limited.Access.to.Healthy.Foods" = "X..Limited.Access.to.Healthy.Foods"
    )
```

```{r}
combined %>%
           group_by(State) %>%
           summarise(total_count = n(), Income_NA_count = sum(is.na(Median.Household.Income)), Uninsured_NA_count = sum(is.na(Perc.Uninsured.Adults)), Tax_NA_count = sum(is.na(Median.Prop.Tax)), Segregation_NA_count = sum(is.na(Residential.Segregation.Index)), Foods_NA_count = sum(is.na(Perc.Limited.Access.to.Healthy.Foods)), Expectancy_NA_count = sum(is.na(Life.Expectancy)), Adequacy_NA_count = sum(is.na(School.Funding.Adequacy)))
```

@@

```{r}
colnames(combined)
```

@@

sub <- combined |> select(c("Life.Expectancy","Residential.Segregation.Index","X..Limited.Access.to.Healthy.Foods","X..Uninsured.Adults","Median.Household.Income", "School.Funding.Cat", "Median.Prop.Tax"))
sub <- unlabel(sub) #unlabel the data (labels cause problem for the mice function)
sub.imp <- mice(sub, m=5, method="pmm", print=FALSE)
```

```{r}
sub.mods <- with(sub.imp, #replace with. model
)
summary(pool(sub.mods))
```
